Proof equivalence in MLL is PSPACE-complete

### 2015-01-30 main/LMCS.tex
finished 3-PART, started NCL section

\begin{definition}
\label{def:proofs to nets}
The relation $(\toNet)$ interprets a proof $\Pi$ by a linking $\links$ as follows: $\Pi\toNet\links$ if for each $\named a\bot$ in $\Pi$, if $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below, then $\links(a)$ is a name in $\Gamma$.
\[
	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
\]
\end{definition}

@@

\begin{remark}
A main distinction with the proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} is that the latter are defined as graphs whose vertices represent inferences, and whose edges represent formulae. This formulation allows an easy inclusion of cuts, which are not present in our proof nets. That the jumps from $\bot$-vertices in these graphs are attached to edges, not vertices, is a natural choice given the categorical view of $\bot$-introduction as the isomorphism $A\to A\pr\bot$.
\end{remark}

@@

Figure~\ref{fig:rewiring} illustrates the rewiring relation in local steps. In the top row, a jump can be rewired across another jump and across a tensor without breaking correctness; these rewiring steps can be seen to correspond to $\bot-\bot$ and $\tn-\bot$ permutations. In the bottom row, rewiring a jump into the par, from $a$ or $b$, only preserves correctness if the jump can be rewired between $a$ and $b$ independently of the par. Intuitively, this corresponds to the $\pr-\bot$ permutation in the following way: the positions that a jump may rewire to correspond to the context of the rule introducing the $\bot$; then to have the premise of the $\pr$-introduction as its context, the jump should be able to rewire to both $a$ and $b$.

@@

A refinement of proof nets introduced by Hughes \cite{Hughes-2012-nets}, is that jumps may be restricted to target only $1$-formulae. For the remainder of the paper, unless otherwise indicated, we will assume that proof nets are of this form.

@@

The salient features of a diagram are the connectedness by $\tn$-edges and containment within a $\pr$-box; respecting these, diagrams may be laid out in the plane in any way that is convenient. More formally, then, sequents and formulae are interpreted as diagrams as follows.

@@

\begin{array}{c@{~}c@{~}c}
	\bot & \Rightarrow & \bullet \\[5pt]
	1	 & \Rightarrow & \circ
\qquad
\begin{array}{rcll}

@@

	& (A_i~\text{not a $\tn$-formula})
\\[5pt]

@@

	& (A_i~\text{not a $\pr$-formula})
\\[5pt]

@@

	& \quad \text{where }A_i~\Rightarrow~

@@

To encode simple numerical properties in \capsabbrev{mll}, our primary tools will be formulae of the form $\bot\tn\dotso\tn\bot$ and $1\pr\dotso\pr1$. In particular, two formulae of the former kind with $i+1$ and $j+1$ $\bot$-occurrences respectively may form a proof net with a formula $1\pr\dotso\pr1$ if and only if the latter counts $i+j+1$ occurrences of the formula $1$. This is illustrated below left for $i=2$ and $j=3$; in the following, we will introduce the abbreviated notation used below right. 
\[
\vc{
  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\foreach \x/\i in {0/a,1/b,2/c,4/d,5/e,6/f,7/g} {\node[bullet] (\i) at (\x,0) {};}
	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
	\draw (a)--(b)--(c) (d)--(e)--(f)--(g);
	\draw[rounded corners] ($(1) + (-.8,-.8)$) rectangle ($(6) + (.8,.8)$);
	\begin{scope}[thepink,->]
			\draw[bend right=10] (a) to (1);
			\draw[bend right=10] (b) to (2);
			\draw[bend right=10] (c) to (3);
			\draw[bend left=10]  (d) to (3);
			\draw[bend left=10]  (e) to (4);
			\draw[bend left=10]  (f) to (5);
			\draw[bend left=10]  (g) to (6);
	\end{scope}
	\node[big_] (A) at (14,0) {$2'$};
	\node[big_] (B) at (16,0) {$3'$};
	\node[big1] (!) at (15,3) {$5'$};
	\draw[rounded corners] ($(!) + (-1.2,-.8)$) rectangle ($(!) + (1.2,.8)$);
	\begin{scope}[thepink,->,big>]
		\draw[bend right=15] (A) to (!);
		\draw[bend left=15]  (B) to (!);
	\end{scope}
  \end{tikzpicture}
}
\]
By $A^n$ we will denote the sequent consisting of $n$ occurrences of a formula $A$. Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\!\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\!\pr\cdots\pr\! A_n$. In diagrammatic notation, a big disc labelled $n'$ will represent the formula $\bigtn(\bot^{n+1})$, and a big circle labelled $n'$ will represent the sequent $\1^{n+1}$. A formula $\bigparr(\1^{n+1})$ is represented by a disc enclosed in a box.

\[
\begin{array}{ccc}
	\1^{n+1}			&\Rightarrow& \bignodes1 \\[5pt]
	\bigparr(\1^{n+1})	&\Rightarrow& \bignodes2 \\[5pt]
	\bigtn(\bot^{n+1})  &\Rightarrow& \bignodes3 \\[5pt]
\end{array}
\qquad\qquad\qquad
\vc{
\begin{tikzpicture}[x=5mm,y=8mm,octo]
	\node[big_] (A) at (-1,2) {};
	\node[big1] (!) at (-1,0) {};
	\node at (.5,1) {$=$};
	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (6,2) -- (7,2) node[bullet] (c) {}; 
	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (7,0) {};
	%\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
	\node at (5,2) {$\dots$}; \node at (5,0) {$\dots$};
	\begin{scope}[thepink,->]
			\draw[big>] (A) to (!);
			\draw[bend right=10] (a) to (1);
			\draw[bend right=10] (b) to (2);
			\draw[bend right=10] (c) to (3);
	\end{scope}
\end{tikzpicture}}
\]
A linking between formulae $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated above right. For the moment, we will not distinguish between the $n!$ different ways in which such a linking can be made, but when the distinction becomes relevant we will make an explicit choice.

@@

An instance of the 3-Partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$, for which the decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$. It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, to relax the problem to ask whether there is a partitioning into \emph{subsets} with sum $k$. The 3-Partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.

A 3-Partition instance $I$ is encoded by a sequent consisting of:
\begin{itemize}
	\item a formula $\bigtn(\bot^{i+1})$ for each $i\in I$, and
	\item the formula $\bigtn(K^n)$ where $K=\bigparr(\1^{k+1})$.
\end{itemize}
The construction, including a proof net providing a solution, is illustrated below.

@@

The idea behind the encoding is that in a proof net, the jumps from a formula for $i$ must connect to the same instance of $K$, since otherwise a switching graph with a cycle is created. The number of $\bot$-occurrences and $1$-occurrences in the sequent then requires that each formula $K$ is linked to by exactly three formulae. A proof net for a sequent that encodes a 3-Partition instance $I$ then directly gives a solution to $I$.

@@

%
\emph{Non-deterministic constraint logic} \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, used here as a convenient tool for \capsabbrev{pspace}-hardness reduction.
%
A \emph{constraint graph} is a graph with weighted edges and an \emph{inflow constraint}---a natural number that may be taken to be always $2$---on each vertex. A \emph{configuration} is an assignment of directions to the edges of the underlying undirected constraint graph. A rewrite step consists of the reversal of a single edge in a configuration, while preserving the condition that the total weight of the incoming edges at each vertex is at least its inflow constraint.

Figure~\ref{fig:NCL example} shows an example rewrite sequence in a part of a constraint graph.
%
The central node has inflow constraint 2, the thick blue edge has weight 2, and the thinner red edges have weight 1.

The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs.
%
A constraint graph may be encoded as a sequent, and a configuration as a proof net.
%
It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.

@@

\begin{figure}
$
~
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,->-] (0,0) -- (3,0);
	\draw[ncl1,->-] (3,0) -- (5,2);
	\draw[ncl1,->-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
\hfill\perm*\,
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,->-] (0,0) -- (3,0);
	\draw[ncl1,-<-] (3,0) -- (5,2);
	\draw[ncl1,->-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
\hfill\perm*\,
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,->-] (0,0) -- (3,0);
	\draw[ncl1,-<-] (3,0) -- (5,2);
	\draw[ncl1,-<-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
\hfill\perm*\,
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,-<-] (0,0) -- (3,0);
	\draw[ncl1,-<-] (3,0) -- (5,2);
	\draw[ncl1,-<-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
~
$

\smallskip
\caption{A series of reconfiguration steps in a constraint graph}
\label{fig:NCL example}
\end{figure}

>>>>

\begin{definition}
\label{def:proofs to nets}
The relation $(\toNet)$ interprets a proof $\Pi$ by a linking $\links$ as follows: $\Pi\toNet\links$ if for each $\named a\bot$ in $\Pi$, $\links(a)$ is a name in $\Gamma$, where $\Gamma$ is the context of the inference introducing $\named a\bot$, as illustrated below.
\[
	\infer[\MLLlabel b]{\Gamma,\named a\bot}{\Gamma}
\]
\end{definition}

@@

\begin{remark}
The proof nets of \cite{Blute-Cockett-Seely-Trimble-1994} may appear to be formulated in quite a distinct way from our presentation, in particular in that their jumps from $\bot$-vertices connect to edges, rather than vertices. The difference is only superficial: in their proof nets, vertices represent inferences, and edges represent formulae; in both presentations, therefore, jumps may be seen to attach to formulae. This way of attaching jumps (to formulae, rather than inferences) is the natural choice also in their setting, which is motivated categorically, where $\bot$-introduction corresponds to the isomorphism $A\to A\pr\bot$.
\end{remark}

@@

The above definition, which is due to Hughes~\cite{Hughes-2012-nets}, gives a ``big-step'' rewrite relation for equivalence. In turn, this rewiring relation is generated by smaller local steps, which correspond more closely to the permutations in the sequent calculus. These smaller steps are illustrated in Figure~\ref{fig:rewiring}. In the top row, a jump can be rewired across another jump and across a tensor without breaking correctness; these rewiring steps can be seen to correspond to $(\bot-\bot)$ and $(\tn-\bot)$ permutations. In the bottom row, rewiring a jump into the par, from $a$ or $b$, only preserves correctness if the jump can be rewired between $a$ and $b$ independently of the par. Intuitively, this corresponds to the $(\pr-\bot)$ permutation in the following way: the positions that a jump may rewire to correspond to the context of the rule introducing the $\bot$; then to have the premise of the $\pr$-introduction as its context, the jump should be able to rewire to both $a$ and $b$.

That the rewiring relation is generated by the small-step relation in Figure~\ref{fig:rewiring} is a main theorem in \cite{Hughes-2012-nets}.

\begin{proposition}[\cite{Hughes-2012-nets}]
Rewiring $(\perm*)$ is generated by the local steps in Figure~\ref{fig:rewiring}.
\end{proposition}

@@

A further refinement in the proof nets introduced by Hughes \cite{Hughes-2012-nets}, is that jumps may be restricted to target only $1$-formulae. For the remainder of the paper, unless otherwise indicated, we will assume that proof nets are of this form.

@@

The salient features of a diagram are the connectedness by $\tn$-edges and containment within a $\pr$-box. Respecting these, we will lay out a diagram in the plane in any way that is convenient, while ensuring (of course) that the layout is kept consistent when comparing different proof nets over the same sequent. More formally, then, sequents and formulae are interpreted as diagrams as follows:

@@

  1\mathrel\Rightarrow\circ, \quad  \bot\mathrel\Rightarrow\bullet, \quad \text{and if}\quad
	A_i~\Rightarrow~
  \quad\text{then}
\begin{array}{@{}rcll@{}}

@@

	& \text{where no $A_i$ is a $\tn$-formula}
\\ \\ 

@@

	& \text{where no $A_i$ is a $\pr$-formula}
\\ \\

@@

	& 

@@

To encode simple numerical properties in \capsabbrev{mll}, our primary tools will be formulae of the form $\bot\tn\dotso\tn\bot$ and $1\pr\dotso\pr1$. In particular, two formulae $A$ and $B$ of the former kind may form a proof net with one $C$ of the latter kind if and only if the total number of $\bot$-occurrences in $A$ and $B$ exceeds the number of $1$-occurrences in $C$ by 1: each 1-occurrence must be linked to by a $\bot$, and one additional $\bot$ is needed to connect $A$ and $B$. We will capture this more generally by counting the number of $\bot$-occurrences in $A$ as $i+1$, so that if $j+1$ is the number of $\bot$-occurrences in $B$, the number of $1$-occurrences in $C$ must be $i+j+1$. Below left is an illustration for $i=2$ and $j=3$. In the following, we will introduce an abbreviated notation, illustrated below right. 
\[
\vc{
  \begin{tikzpicture}[x=5mm,y=-5mm,octo]
	\foreach \x/\i in {0/a,1/b,2/c,4/d,5/e,6/f,7/g} {\node[bullet] (\i) at (\x,0) {};}
	\foreach \i in {1,...,6} {\node[circ] (\i) at (\i,3) {};}
	\draw (a)--(b)--(c) (d)--(e)--(f)--(g);
	\draw[rounded corners] ($(1) + (-.8,-.8)$) rectangle ($(6) + (.8,.8)$);
	\begin{scope}[thepink,->]
			\draw[bend right=10] (a) to (1);
			\draw[bend right=10] (b) to (2);
			\draw[bend right=10] (c) to (3);
			\draw[bend left=10]  (d) to (3);
			\draw[bend left=10]  (e) to (4);
			\draw[bend left=10]  (f) to (5);
			\draw[bend left=10]  (g) to (6);
	\end{scope}
	\node[big_] (A) at (14,0) {$2'$};
	\node[big_] (B) at (16,0) {$3'$};
	\node[big1] (!) at (15,3) {$5'$};
	\draw[rounded corners] ($(!) + (-1.2,-.8)$) rectangle ($(!) + (1.2,.8)$);
	\begin{scope}[thepink,->,big>]
		\draw[bend right=15] (A) to (!);
		\draw[bend left=15]  (B) to (!);
	\end{scope}
  \end{tikzpicture}
}
\]
By $A^n$ we will denote the sequent consisting of $n$ occurrences of a formula $A$. Given a sequent $\Gamma=A_1,\dotsc,A_n$ we will write $\bigtn\Gamma$ for $A_1\!\tn\cdots\tn A_n$, and $\bigparr\Gamma$ for $A_1\!\pr\cdots\pr\! A_n$. In diagrammatic notation, a big disc labelled $n'$ will represent the formula $\bigtn(\bot^{n+1})$, and a big circle labelled $n'$ will represent the sequent $\1^{n+1}$. A formula $\bigparr(\1^{n+1})$ is represented by a disc enclosed in a box. This extends our diagrammatic notation as follows.

\[
\begin{array}{ccc}
	\1^{n+1}			&\Rightarrow& \bignodes1 \\[10pt]
	\bigparr(\1^{n+1})	&\Rightarrow& \bignodes2 \\[10pt]
	\bigtn(\bot^{n+1})  &\Rightarrow& \bignodes3 \\[10pt]
\end{array}
\qquad\qquad\qquad
\vc{
\begin{tikzpicture}[x=5mm,y=8mm,octo]
	\node[big_] (A) at (-1,2) {};
	\node[big1] (!) at (-1,0) {};
	\node at (.5,1) {$=$};
	\draw (2,2) node[bullet] (a) {} -- (3,2) node[bullet] (b) {} -- (4,2) (6,2) -- (7,2) node[bullet] (c) {}; 
	\node[circ] (1) at (2,0) {}; \node[circ] (2) at (3,0) {}; \node[circ] (3) at (7,0) {};
	%\draw[dotted] (4,2)--(5,2) (4,0)--(5.1,0);
	\node at (5,2) {$\dots$}; \node at (5,0) {$\dots$};
	\begin{scope}[thepink,->]
			\draw[big>] (A) to (!);
			\draw[bend right=10] (a) to (1);
			\draw[bend right=10] (b) to (2);
			\draw[bend right=10] (c) to (3);
	\end{scope}
\end{tikzpicture}}
\]
A linking between formulae $\bigtn(\bot^n)$ and $\bigparr(\1^n)$ will be represented by a wide arrow, as illustrated above right. For the moment, we will not distinguish between the $n!$ different ways in which such a linking can be made, but when the distinction becomes relevant we will make an explicit choice.

@@

An instance of the 3-Partition problem is given by a multiset $I=\{i_1,\dotsc,i_{3n}\}$ of $3n$ natural number values with total sum $\sum I=nk$. The decision problem asks whether a partitioning exists of $I$ into $n$ triples $(i_a,i_b,i_c)$ each with sum $k$. It may be assumed that each $i\in I$ lies between $\nicefrac k4$ and $\nicefrac k2$, so that any partitioning into \emph{subsets} with sum $k$ is a solution, since each subset of sum $k$ necessarily has $3$ elements. The 3-Partition problem is strongly \capsabbrev{np}-complete \cite{GareyAndJohnson}, which means it remains \capsabbrev{np}-complete with a unary encoding of the values in $I$.

We will give a simple encoding of 3-partition in MLL proof search, similar to those of Kanovich \cite{Kanovich-1992} and Lincoln and Winkler \cite{Lincoln-Winkler-1994}. A 3-Partition instance $I$ is encoded by a sequent consisting of:
\begin{itemize}
	\item a formula $\bigtn(\bot^{i+1})$ for each $i\in I$, and
	\item the formula $\bigtn(K^n)$ where $K=\bigparr(\1^{k+1})$.
\end{itemize}
A solution to the 3-partition problem is encoded as a proof net as follows. If the numbers $a$, $b$, and $c$ are assigned to a triple corresponding to a formula $K_j$, then the corresponding formulae have $a+1$, $b+1$, and $c+1$ occurrences of $\bot$, and $k+1=a+b+c+1$ occurrences of $\1$, respectively. Then as described previously, there is a proof net for these formulae, obtained by attaching each jump to a distinct $\1$, with the exception of three jumps, one each from $a$, $b$, and $c$, overlapping on exactly one intance.

The construction is illustrated below, where the numbers $i$ are conveniently ordered to give the solution $(i_1,i_2,i_3)$, $(i_4,i_5,i_6)$, etc.

@@

The correctness condition ensures that every proof net on a sequent encoding a 3-partition problem gives a solution that problem. If two jumps from a formula encoding a number $i$ connect to different formulae $K_j$ and $K_m$, a cycle is created immediately. Thus, the jumps from each $i$ must all connect to the same $K$, and the number of occurrences of $\bot$ and $\1$ in the encoding then ensures that when the formulae for $i_a$, $i_b$, and $i_c$, connect to one formulae $K$, their values sum to $k$, $i_a+i_b+i_c=k$.

The encoding of 3-partition serves to illustrate how simple numerical constraints can be encoded in proof nets: by matching up a given number of $\bot$-occurrences and $\1$-occurrences and by separating formulae of the form $\bigparr(\1^n)$ by a tensor. This idea will form the basis of our encoding of non-deterministic constraint logic. First, we will introduce the latter.

@@

\emph{Non-deterministic constraint logic} (NCL) \cite{Hearn-Demaine-2005,Demaine-Hearn-2008,GamesPuzzlesAndComputation} is a simple graph-rewriting formalism, introduced as a convenient tool for \capsabbrev{pspace}-hardness reduction. It is exactly for this purpose that we shall use it.

The graphs of NCL, called \emph{constraint graphs}, have directed, weighted edges, and a rewrite step (or \emph{move}) consists of reversing the direction of exactly one edge. Each vertex in a constraint graph has an \emph{inflow constraint}, a natural number value, and moves are required to preserve the property that the \emph{inflow} at each vertex, the sum weight of its incoming edges, never drops below the inflow constraint (i.e.\ the inflow constraint dictates a \emph{minimum} inflow).

The specific problem we will use is the \emph{configuration--to--configuration} problem, which asks whether a path of rewrite steps exists between two constraint graphs. This problem is PSPACE-complete, and remains so under various restrictions: inflow constraints can be fixed at the value 2, edge weights can be restricted to the value 1 and 2, the graphs can be required to be planar, and loops and double edges (edges connecting the same 2 vertices) can be prohibited, for example.

We will need no such restrictions, and will encode the general case. However, for simplicity of exposition, in the examples of constraint graphs in this section we will use the following conventions. Edges will have weight 1 or 2; those of weight 1 are drawn as thin red arrows, and those of weight 2 as thicker blue arrows. Vertices with inflow constraint 2 are drawn as grey circles. For convenience, we will assume that dangling edges are connected to vertices of weight 0, which are omitted from illustrations.

An example rewrite sequence is given in Figure~\ref{fig:NCL example}. This particular specimen encodes a logical conjunction, and is not unlike an \textsc{and}-gate: in order to invert the weight 2 edge on the right, both weight 1 edges on the left must be inverted first.

\begin{figure}
\[
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,->-] (0,0) -- (3,0);
	\draw[ncl1,->-] (3,0) -- (5,2);
	\draw[ncl1,->-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
\quad\perm*\quad
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,->-] (0,0) -- (3,0);
	\draw[ncl1,-<-] (3,0) -- (5,2);
	\draw[ncl1,->-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
\quad\perm*\quad
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,->-] (0,0) -- (3,0);
	\draw[ncl1,-<-] (3,0) -- (5,2);
	\draw[ncl1,-<-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
\quad\perm*\quad
\vc{\begin{tikzpicture}[x=-3mm,y=3mm]
	\draw[ncl2,-<-] (0,0) -- (3,0);
	\draw[ncl1,-<-] (3,0) -- (5,2);
	\draw[ncl1,-<-] (3,0) -- (5,-2);
	\node[nclnode] at (3,0) {};
\end{tikzpicture}}
\]
\caption{A series of reconfiguration steps in a constraint graph}
\label{fig:NCL example}
\end{figure}

%
A constraint graph may be encoded as a sequent, and a configuration as a proof net.
%
It is useful for us to generalise the notion of configuration a little: we will allow \emph{partial} configurations, where edges may be left undirected---as long as the inflow constraints are satisfied by the directed edges.

@@
